Austrian Parliament: MPs transparency and conflict of interest report

### 2021-02-17 _post/2020-07-21-austrian-parliament-mps-transparency-and-conflict-of-interest-report/austrian-parliament-mps-transparency-and-conflict-of-interest-report.Rmd
css remove line
without theme

author:
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    orcid_id: 0000-0002-6897-1693
categories:
  - Austria
  - OCR
  - web scraping

@@

knitr::opts_chunk$set(
  echo = TRUE,
  fig.align = "left",
  # fig.height = 5,
  # fig.width = 7,
  out.width = "100%",
  message = FALSE,
  warning = FALSE,
  dpi = 300
)

@@

<details closed> 
<summary>Code: Define plot theme</summary> 
```{r echo=TRUE}
theme_post <- function() {
  hrbrthemes::theme_ipsum_rc() +
    theme(
      plot.margin = margin(l = 0, unit = "cm"),
      plot.title = element_markdown(
        color = "grey20",
        face = "bold",
        margin = margin(l = 0, unit = "cm"),
        size = 13
      ),
      plot.title.position = "plot",
      plot.subtitle = element_text(
        color = "grey50",
        margin = margin(t = 0.2, b = 0.3, unit = "cm"),
        size = 11
      ),
      plot.caption = element_text(
        color = "grey50",
        size = 8,
        hjust = c(0)
      ),
      plot.caption.position = "panel",
      axis.title.x = element_text(angle = 0,
                                         color="grey50",
                                         hjust=1),
      axis.text.x = element_text(size = 9, 
                                 color = "grey50"),
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 9,
                                 color="grey50"),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.spacing = unit(0.25, "cm"),
      panel.spacing.y = unit(0.25, "cm"),
      strip.text = element_text(
        angle = 0,
        size = 9,
        vjust = 1,
        face = "bold"
      ),
      legend.title = element_text(
        color = "grey30",
        face = "bold",
        vjust = 1,
        size = 7
      ),
      legend.text = element_text(
        size = 7,
        color = "grey30"
      ),
      legend.justification = "left",
      legend.box = "horizontal", # arrangement of multiple legends
      legend.direction = "vertical",
      legend.margin = margin(l = 0, t = 0, unit = "cm"),
      legend.spacing.y = unit(0.07, units = "cm"),
      legend.text.align = 0,
      legend.box.just = "top",
      legend.key.height = unit(0.2, "line"),
      legend.key.width = unit(0.5, "line"),
      text = element_text(size = 5)
    )
}

@@

![](/post/2020-07-03-austrian-parliament-mps-transparency-and-conflict-of-interest-report_files/list_example - Copy.PNG){width=100%}

@@

@@

```{r echo=FALSE}
pl_gender_category

>>>>

author:
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    orcid_id: 0000-0002-6897-1693

categories:
  - Austria
  - OCR
  - web scraping

@@

knitr::opts_chunk$set(
  echo = TRUE,
  fig.align = "left",
  # fig.height = 5,
  # fig.width = 7,
  out.width = "100%",
  message = FALSE,
  warning = FALSE
)

@@

<details closed> 
<summary>Code: Define plot theme</summary> 
```{r echo=F}
plot_bg_color <- readr::read_file(file=here::here("theme.css")) %>% 
  str_extract(., regex("(?<=blog-bg-color:).*?(?=;)")) %>%
  str_trim() %>% 
  str_extract(., regex("^#\\S+"))

theme_post2 <- function() {
  hrbrthemes::theme_ipsum_rc() +
    theme(
      plot.background = element_rect(fill = plot_bg_color, color=NA),
      panel.background = element_rect(fill = plot_bg_color, color=NA),
      plot.margin = margin(l = 0, unit = "cm"),
      plot.title = element_markdown(
        color = "grey20",
        face = "bold",
        margin = margin(l = 0, unit = "cm"),
        size = 13
      ),
      plot.title.position = "plot",
      plot.subtitle = element_text(
        color = "grey50",
        margin = margin(t = 0.2, b = 0.3, unit = "cm"),
        size = 11
      ),
      plot.caption = element_text(
        color = "grey50",
        size = 8,
        hjust = c(0)
      ),
      plot.caption.position = "panel",
      axis.title.x = element_text(angle = 0,
                                         color="grey50",
                                         hjust=1),
      axis.text.x = element_text(size = 9, 
                                 color = "grey50"),
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 9,
                                 color="grey50"),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.spacing = unit(0.25, "cm"),
      panel.spacing.y = unit(0.25, "cm"),
      strip.text = element_text(
        angle = 0,
        size = 9,
        vjust = 1,
        face = "bold"
      ),
      legend.title = element_text(
        color = "grey30",
        face = "bold",
        vjust = 1,
        size = 7
      ),
      legend.text = element_text(
        size = 7,
        color = "grey30"
      ),
      legend.justification = "left",
      legend.box = "horizontal", # arrangement of multiple legends
      legend.direction = "vertical",
      legend.margin = margin(l = 0, t = 0, unit = "cm"),
      legend.spacing.y = unit(0.07, units = "cm"),
      legend.text.align = 0,
      legend.box.just = "top",
      legend.key.height = unit(0.2, "line"),
      legend.key.width = unit(0.5, "line"),
      text = element_text(size = 5)
    )
}

theme_post <- function() {
  hrbrthemes::theme_ipsum_rc() +
    theme(
      plot.background = element_rect(fill = plot_bg_color, color=NA),
      panel.background = element_rect(fill = plot_bg_color, color=NA),
      #panel.border = element_rect(colour = plot_bg_color, fill=NA),
      #plot.border = element_rect(colour = plot_bg_color, fill=NA),
      plot.margin = margin(l = 0, 
                           t = 0.25,
                           unit = "cm"),
      plot.title = element_markdown(
        color = "grey20",
        face = "bold",
        margin = margin(l = 0, unit = "cm"),
        size = 13
      ),
      plot.title.position = "plot",
      plot.subtitle = element_text(
        color = "grey50",
        margin = margin(t = 0.2, b = 0.3, unit = "cm"),
        size = 11
      ),
      plot.caption = element_text(
        color = "grey50",
        size = 8,
        hjust = c(0)
      ),
      plot.caption.position = "panel",
      axis.title.x = element_text(
        angle = 0,
        color = "grey50",
        hjust = 1
      ),
      axis.text.x = element_text(
        size = 9,
        color = "grey50"
      ),
      axis.title.y = element_blank(),
      axis.text.y = element_text(
        size = 9,
        color = "grey50"
      ),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.spacing = unit(0.25, "cm"),
      panel.spacing.y = unit(0.25, "cm"),
      strip.text = element_text(
        angle = 0,
        size = 9,
        vjust = 1,
        face = "bold"
      ),
      legend.title = element_text(
        color = "grey30",
        face = "bold",
        vjust = 1,
        size = 9
      ),
      legend.text = element_text(
        size = 9,
        color = "grey30"
      ),
      legend.justification = "left",
      legend.box = "horizontal", # arrangement of multiple legends
      legend.direction = "vertical",
      legend.margin = margin(l = 0, t = 0, unit = "cm"),
      legend.spacing.y = unit(0.07, units = "cm"),
      legend.text.align = 0,
      legend.box.just = "top",
      legend.key.height = unit(0.2, "line"),
      legend.key.width = unit(0.5, "line"),
      text = element_text(size = 5)
    )
}

@@

![](austrian-parliament-mps-transparency-and-conflict-of-interest-report_files/list_example - Copy.PNG){width=100%}

@@

pl_gender_category

@@

```{r echo=FALSE, fig.height=6, fig.width=10, include=T}
pl_gender_category
